---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# <i class="fas fa-globe-europe" aria-hidden="true"> </i> Micro4all
<!-- badges: start -->
<!-- badges: end -->

The goal of *micro4all* is to unify all functions used in our laboratory to get a complete analysis of amplicon data for microbial community studies. It includes several useful tools, as an *automatized detection of MOCK community* and calculation of *community cut-off* as well as loops for statistical analysis.  

## <i class="fas fa-cogs" aria-hidden="true"></i> Installation

You can install *micro4all* directly from GitHub with:

```{r,eval=FALSE}
devtools::install_github("nuriamw/micro4all")
```

## <i class="fas fa-info-circle" aria-hidden="true"></i> How to use it?

Along with this package, a full and detailed workflow has been created. There, you can find our usual pipeline for data analysis and examples of *micro4all* functions. Check the tutorial [here](https://nuriamw.github.io/micro4all/tutorial/package_workflow.html) 
